### 2025-04-10 manuscript.Rmd
Update manuscript.Rmd

Once the document is reredered, that is, generated a second time, and the reproducibility metadata file exists, the computations in the code chunk are rerun, and their results are compared to the stored reproducibility information for each variable.
The reproducibility report will then detail the success of each reproduction attempt.
In our example, the computation was successfully reproduced.
A snippet from the resulting generated document is displayed in Figure \@ref(fig:rstudioscreen3).

>>>>

Once the document is rendered a second time, and the reproducibility metadata file exists, the computations in the code chunk are rerun, and their results are compared to the stored reproducibility information for each variable.
The reproducibility report will then detail the success of each reproduction attempt.
In our example, the computation was successfully reproduced.
A snippet from the resulting generated document is displayed in Figure \@ref(fig:rstudioscreen3).
